A thesis draft

### 2018-11-27 res/sections/15-ArchitecturalImplementation.tex
Add introduction on chapter 5

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.5]{Architecture}
  \caption[Architecture schema depicting the expected
    implementation]{Architecture schema depicting the expected implementation.
    It is possible to see how Openbaton interacts with the various components in
    the architecture, and how RabbitMQ is used as a message broker between the
    different parts to enable message exchanging.}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.5]{Attempt1}
  \caption[Fist attempt components organization schema]{Fist attempt components
    organization schema. We can see how the main Openstack role is to deploy and
    manage the resources, while Openbaton has the role of management and
    orchestration. Finally, RabbitMQ sends and receives status update from the
    EMS for every VNF deployed.}
  \label{chap:archimpl:sec:fistattempt:img:schema1}
\end{figure}

@@

\subsection{Kubernetes configuration}

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.25]{kubernetes-control-plane}
  \caption[Kubernetes control plane schema]{Kubernetes control plane
    schema~\cite{k8scp}. It is possible to denote important components in the
    Kubernetes Control plane. In this high-level component architecture the
    master keeps an internal database, \emph{etcd}, the entry point for the API
    Server and the Pod scheduler. The nodes instead contain the kubelet daemon,
    the container runtime and the networking configuration.}
  \label{chap:archimpl:sec:secondattempt:img:k8scp}
\end{figure}

>>>>

\section{Architecture introduction}
Before describing the real implementation, we are going to briefly introduce
some of its functional components and the way they work.

\subsection{A two-level orchestration framework}
\begin{figure}[t]
  \centering
  \includegraphics[scale=0.5]{Architecture}
  \caption[Architecture schema depicting the expected
    implementation]{Architecture schema depicting the expected implementation.
    It is possible to see how Openbaton interacts with the various components in
    the architecture, and how RabbitMQ is used as a message broker between the
    different parts to enable message exchanging.}
  \label{chap:archimpl:sec:fistattempt:img:architecture}
\end{figure}

It is important to keep in consideration that the ETSI NFV architectural
framework is to be considered service and/or application agnostic. This excludes
this framework from the burden of being application aware for NS configuration
and management and for the VNF application layer configuration and management.

The lack of these two management requires a service aware software, that has the
task to perform service lifecycle management and monitoring via the API offered
by the ETSI MANO. In this context, is possible to identify two different type of
orchestrator, as represented in
Figure~\ref{chap:archimpl:sec:fistattempt:img:architecture}:
\begin{itemize}
\item a high layer, service-aware;
\item a low layer, service-unaware.
\end{itemize}
Both the layer would use Openbaton. The messages would be exchanged through
RabbitMQ, using the Advance Message Queuing Protocol (AMQP).

\paragraph*{Low-layer orchestrator}
The low-layer orchestrator jobs corresponds to the one defined in the ETSI MANO
definition, with the role of managing and orchestrating VNFs and NSs. The
low-layer MANO holds different data repositories where VNF and NS definitions
are stored, various monitoring tools and logs and the network services
repository. The low layer MANO exposes a set of APIs to the upper layer (related
to handling services) MANO, that is able to configure and manage the services.
In other words, the service MANO has the possibility to configure and launch
services to the low-layer orchestrator, providing the necessary information.

\subsection{Low-layer functional components}
In the following section we are going to briefly talk about the role of the most
peculiar components in the defined architecture. A description of the tasks that
the components have to abide in the ETSI MANO architecture is available in
Section~\ref{chap:archimpl:sec:secondattempt:sec:k8s}.
\begin{description}
\item[VNFM] As is possible to see from the
  Figure~\ref{chap:archimpl:sec:fistattempt:img:architecture}, the following
  architecture envisages the possibility of multiple VNFM components, required
  for the control and management of different virtualized functions. In
  particular, the use of different and specialized VNFMs allows to control and
  manage different functional aspects of the control/data plan.
\item[Network service management] in this architectural proposal, it corresponds
  the the brain of the infrastructure MANO, where service instantiation and
  lifecycle management happens. This part interacts with the VNFM/VIM and with
  the RabbitMQ middleware. In this context, the NFVO is involved in chaining the
  required VNFs in order to create the service delivery path. Inside this
  component is possible to identify the Service Lifecycle Management, that
  listens to status report coming from the VNFM and thus generating logs and
  monitoring information.
\item[Monitoring and Information Management] this block gathers data from the
  data layers (identified in the image as the repository), which can be object
  of consultation from other applications.
\end{description}

From now on we are going to describe out attempt in implementing the
aforementioned architectural proposal, and we will describe the challenges and
the issue we encountered.

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.5]{Attempt1}
  \caption[Fist attempt components organization schema]{Fist attempt components
    organization schema. We can see how the main Openstack role is to deploy and
    manage the resources, while Openbaton has the role of management and
    orchestration. Finally, RabbitMQ sends and receives status update from the
    EMS for every VNF deployed.}
  \label{chap:archimpl:sec:fistattempt:img:schema1}
\end{figure}

@@

\subsection{Kubernetes configuration}
\label{chap:archimpl:sec:secondattempt:sec:k8s}
\begin{figure}[t]
  \centering
  \includegraphics[scale=0.25]{kubernetes-control-plane}
  \caption[Kubernetes control plane schema]{Kubernetes control plane
    schema~\cite{k8scp}. It is possible to denote important components in the
    Kubernetes Control plane. In this high-level component architecture the
    master keeps an internal database, \emph{etcd}, the entry point for the API
    Server and the Pod scheduler. The nodes instead contain the kubelet daemon,
    the container runtime and the networking configuration.}
  \label{chap:archimpl:sec:secondattempt:img:k8scp}
\end{figure}
